Merging Datasets Through Deep learning

### 2018-08-30 paper2018/relatedWork.tex
related work

The idea of building joint embeddings for merging followed by nearest neighbors search has been applied recently to a slightly different problem of linking relational tuple embeddings with embeddings of other relational tuples or unstructured text \cite{Bordawekar18}, \cite{IDEL18}).  For the problem of linking tuples, each model that is learnt is specific to the database it was trained on.  Our contribution is that we developed general purpose embedding models for merging alternate surface forms of key entities such as people and companies leveraged from linked open data.  Once such models are built, they can be applied to joining any two datasets that share that semantic type.

TBD - related work on triplet selection and losses.

>>>>

The idea of building joint embeddings for merging followed by nearest neighbors search has been applied recently to the problem of linking relational tuple embeddings with embeddings of other relational tuples or unstructured text \cite{Bordawekar18}, \cite{IDEL18}).  For the problem of linking tuples, each model that is learnt is specific to the database it was trained on.  Our contribution is that we developed general purpose embedding models for merging alternate surface forms of key entities such as people and companies leveraged from linked open data.  Once such models are built, they can be applied to joining any two datasets that share that semantic type.

Metric learning is a well studied problem in the face recognition literature, e.g., \cite{DBLP:conf/cvpr/2014}, \cite{DBLP:conf/cvpr/SchroffKP15}, with a rich literature in triplet mining techniques.  The closest approach to ours is the use of nearest neighbors algorithms for triplet mining has been applied by \cite{DBLP:journals/corr/KumarHC0D17}, but their focus is on a common practice in the literature which is focusing on mining semi-hard negatives, that is focusing on negatives where at least one positive is closer to the anchor.  In general, this means that one cannot look at fixed neighborhood sizes in building triplets.  In other words, if all the positives are further away from the anchor than the negatives in a given neighborhood size of $k$, it means that $k$ needs to be expanded until a neighborhood size is found that has the right characteristics (i.e., at least one positive that is closer than the negatives which can be chosen).  Our approach much more efficient because it relies on a fixed $k$ to generate samples, and shows that at least in the names domain, learning with hard negatives is effective.

The study of loss function effectiveness in metric learning is also a rich literature, with two basic types of loss functions that have been proposed: (a) local loss functions such as triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, angular loss \cite{Zhang:2016:DML:3088616.3088665} and improved loss \cite{DBLP:journals/corr/abs-1708-01682}, and (b) loss functions that operate on a more global level across a batch of training examples \cite{NIPS2016_6200}, \cite{songCVPR17}.  Our focus in this paper is on local loss functions.
